Mapping malaria in pre-elimination settings by sharing spatial information between incidence and prevalence datasets

### 2019-08-06 si.tex
Tidy up.

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_random_preds.png}}
\caption{\label{predobsmapsen}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}
\end{figure}

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.9\textwidth]{figures/mdg_both_cv12_random_preds.png}}
\caption{\label{predobsmapsen}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}
\end{figure}

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 1\textwidth]{figures/sen_both_cv12_random_preds.png}}
\caption{\label{predobsmapsen}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}
\end{figure}

\clearpage
\subsection{Spatial CV predictions}

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.8\textwidth]{figures/idn_both_cv12_preds.png}}
\caption{\label{predobsmapsen}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}
\end{figure}

@@

\caption{Predictions from the baseline model fitted to all data in Madagascar.}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{Predictions from the prevalence GP model fitted to all data in Madagascar.}
\end{figure}

@@

\caption{Predictions from the joint model fitted to all data in Madagascar.}
\end{figure}

@@

\caption{Predictions from the baseline model fitted to all data in Senegal.}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{Predictions from the prevalence GP model fitted to all data in Senegal.}
\end{figure}

@@

\caption{Predictions from the joint model fitted to all data in Senegal.}
\end{figure}

@@

\caption{Predictions from the baseline model fitted to all data in Indonesia.}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{Predictions from the prevalence GP model fitted to all data in Indonesia.}
\end{figure}

@@

\caption{Predictions from the joint model fitted to all data in Indonesia.}
\end{figure}

@@

\caption{The prevalence GP model that is used as a covariate.}
\end{figure}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{The random field as fitted to all the data in the prevalence GP model.}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\end{figure}

@@

\caption{The prevalence GP model that is used as a covariate.}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\end{figure}

@@

\caption{The prevalence GP model that is used as a covariate.}
\end{figure}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{The random field as fitted to all the data in the prevalence GP model.}
\end{figure}

>>>>

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_random_preds.png}}
\caption{\label{predobsmapsen1}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}
\end{figure}

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 0.9\textwidth]{figures/mdg_both_cv12_random_preds.png}}
\caption{\label{predobsmapsen2}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}
\end{figure}

\begin{figure}[h!]
% to be removed before submission
\makebox{\includegraphics[width = 1\textwidth]{figures/sen_both_cv12_random_preds.png}}
\caption{\label{predobsmapsen3}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for random cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}
\end{figure}

@@

\caption{Predictions from the baseline model fitted to all data in Madagascar.}
\label{baselinemdg}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{Predictions from the prevalence GP model fitted to all data in Madagascar.}
\label{gpmdg}
\end{figure}

@@

\caption{Predictions from the joint model fitted to all data in Madagascar.}
\label{jointmdg}
\end{figure}

@@

\caption{Predictions from the baseline model fitted to all data in Senegal.}
\label{baselinesen}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{Predictions from the prevalence GP model fitted to all data in Senegal.}
\label{gpsen}
\end{figure}

@@

\caption{Predictions from the joint model fitted to all data in Senegal.}
\label{jointsen}
\end{figure}

@@

\caption{Predictions from the baseline model fitted to all data in Indonesia.}
\label{baselineidn}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{Predictions from the prevalence GP model fitted to all data in Indonesia.}
\label{gpidn}
\end{figure}

@@

\caption{Predictions from the joint model fitted to all data in Indonesia.}
\label{jointidn}
\end{figure}

@@

\caption{The prevalence GP model that is used as a covariate.}
\label{gpsencov}
\end{figure}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\label{baselinefieldsen}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{The random field as fitted to all the data in the prevalence GP model.}
\label{gpfieldsen}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\label{jointfieldsen}
\end{figure}

@@

\caption{The prevalence GP model that is used as a covariate.}
\label{gpidncov}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\label{baselinefieldidn}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\label{gpfieldidn}
\end{figure}

@@

\caption{The random field as fitted to all the data in the joint model.}
\label{jointfieldidn}
\end{figure}

@@

\caption{The prevalence GP model that is used as a covariate.}
\label{gpmdgcov}
\end{figure}

@@

\caption{The random field as fitted to all the data in the baseline model.}
\label{baselinefieldmdg}
\end{figure}
\begin{figure}[h!]
\centering

@@

\caption{The random field as fitted to all the data in the prevalence GP model.}
\label{gpfieldmdg}
\end{figure}
